Efficient Selection of Time Series Shapelets

### 2024-04-16 Docs/paper/main.tex
Preliminaries

Regardless of the technique used in order to select the candidates, the 
evaluation in the above approaches was done using the information gain.
Lines et al.~\cite{alternative_measures} were the first to consider using
different evaluation methods instead of the information gain. They considered
as evaluation measures statistical tests to verify if points from the same
distribution or not, such as Kruskal Wallis and Mood's medians. On another 
the same authors use the ANOVA F-statistic~\cite{shapelet_transform} as an 
evaluation measure, which was not significantly better than the information 
gain, but on average, shapelets selected using the F-statistic resulted in high
classification accuracy.

@@

\section{Preliminaries}

\section{Selection}

>>>>

Regardless of the technique used in order to select the candidates, the
evaluation in the above approaches was done using the information gain.
Lines et al.~\cite{alternative_measures} were the first to consider using
different evaluation methods instead of the information gain. They considered
as evaluation measures statistical tests to verify if points from the same
distribution or not, such as Kruskal Wallis and Mood's medians. On another
the same authors use the ANOVA F-statistic~\cite{shapelet_transform} as an
evaluation measure, which was not significantly better than the information
gain, but on average, shapelets selected using the F-statistic resulted in high
classification accuracy.
A recent work~\cite{silhoutte_shapelets} proposed the usage of Silhouettes
\cite{silhouettes} as an evaluation measure, the results were competitive with
the F-statistic and information gain, but the silhouette had much better results
when the number of shapelets used to classify was small.

@@

\section{Preliminaries}
This section defines the key concepts used in the paper.
\begin{definition}[Time Series]
	A time series $T$ is sequence of $n$ consecutive real numbers:
	$T = [T_1, T_2, \dots, T_n]$.
\end{definition}

\begin{definition}[Subsequence]
	A subsequence of length $l$ from a time series $T$ starting from position $i$
	is an ordered set of consecutive values from $T$ denoted as:
	$S_{i, l} = [T_i, T_{i+1},, \dots, T_{i+l-1}]$.
\end{definition}

\begin{definition}[Sliding window]
	A sliding window of length $l$ over a time series $T$ is the set of
	all subsequences of length $l$ extracted from $T$:
	$W_T^l = [S_{1, l}, S_{2, l}, \dots S_{n-l+1, l}]$.
\end{definition}

A dataset consists of $m$ time series, each having a class label $c \in [1, 2,
		\dots, K]$. The sliding windows $W_T^l$ all have the same class label $c$ of the
time series $T$ they were extracted from. To compute the evaluation score of
each window using the Silhouette, we need first to introduce a (dis-)similarity
measure. In this work, we consider the normalized Euclidean distance:

\begin{definition}[Normalized Euclidean distance]
	The normalized Euclidean distance between two subsequences $S$ and $Q$ of
	length $l$:
	$$d(S, Q) = \sqrt{\sum_{i=1}^l (\frac{S_i - \mu_S}{\sigma_S} - \frac{Q_i -
				\mu_Q}{\sigma_Q})^2}$$
	where $\mu_S$ and $\sigma_S$ represent the mean and standard deviation of
	$S$ respectively.
\end{definition}

Finally, we define the silhouette score for a subsequence:

\begin{definition}[Silhouette score of a subsequence]
	Given a set $\mathcal{D}$ of subsequences (sliding windows) and their
	corresponding labels, the silhouette score for a subsequence $S_i$ having label
	$c$ is:
	$$
		s(S_i) = \frac{b - a}{\max{(a, b)}}
	$$
	where:
	\begin{itemize}
		\item $b = \frac{\sum_{j \in I \setminus I_c}d(S_i, S_j)}{|I \setminus I_c|}$,
		\item $a = \frac{\sum_{k \in I_c}d(S_i, S_k)}{|I_c|}$,
		\item $I$ is the set of indices of all subsequences in $\mathcal{D}$, and
		\item $I_c$ is the set of indices of subsequences having label $c$.
	\end{itemize}
\end{definition}

Notice, that our definition of the silhouette, the term $b$ considers all 
subsequences from other classes instead of only considering only the class that
is closest to the subsequence $S_i$.
